### 2017-02-10 conclusion.tex
Minor corrections

\begin{figure}
  \includegraphics[width=\textwidth]{conclusion.pdf}
  \caption[Irregularity production factors]{{\:}Irregularity production factors\\ Summary of the main conclusions in this thesis.  The radar of interest (MCM) is highlighted in pink.  Polar patches (orange) drift antisunwards across the polar cap following the background plasma convection (red contours).  Nighttime irregularity observation is enhanced for a positive IMF \(B_y\) component.  Production is maximized near the terminator.  Small-scale irregularity production surrounding a large-scale structure is found to exhibit both asymmetry and anisotropy.  Radars are most likely to observe this asymmetry if the patch is elongated along the radar boresight.  Backscatter is most likely to be observed in a particular window of slant ranges within the radar FoV.}
  \label{fig:conclusion}
\end{figure}

One other result presented in Chapter \ref{sec:paper1} was that nighttime occurrence of FAIs was also higher for time intervals with a positive IMF \(B_y\) component, Figure \ref{fig:conclusion}.  This could be due to the control that the \(B_y\) component exerts over ionospheric convection patterns, as explained below.  In a classical two-cell convection pattern with predominantly negative IMF \(B_z\), the plasma flows antisunward from dayside to nightside across the terminator.  In this configuration, the plasma flow, \(\vec{V}_E\), and the density gradient, \(\vec{G}\), are antiparallel, the least favorable orientation for GDI growth.  However, with a significant IMF \(B_y\) component, the orientation of the convection cells rotates such that plasma no longer convects directly antisunward, creating a situation where GDI is more favorable and plasma structures can develop more readily.  Additionally, a significant IMF \(B_y\) component can contribute to the formation of polar patches by creating convection perturbations that separate high density patches from the daytime reservoir, as described in Section \ref{sec:lit_patches}.  In this way, the IMF \(B_y\) component may be indirectly responsible for the increased observation of backscatter.  If patch occurrence increases, it can contribute to the nighttime background density, as described above, which can improve propagation conditions so that FAIs can be observed by 
HF radars.

>>>>

\begin{figure}
  \includegraphics[width=\textwidth]{conclusion.pdf}
  \caption[Irregularity production factors]{{\:}Irregularity production factors\\ Summary of the main conclusions in this thesis.  The radar of interest (MCM) is highlighted in pink.  Polar patches (orange) drift antisunwards across the polar cap following the background plasma convection (red contours).  Nighttime irregularity observation is enhanced for a negative IMF \(B_y\) component.  Production is maximized near the terminator.  Small-scale irregularity production surrounding a large-scale structure is found to exhibit both asymmetry and anisotropy.  Radars are most likely to observe this asymmetry if the patch is elongated along the radar boresight.  Backscatter is most likely to be observed in a particular window of slant ranges within the radar FoV.}
  \label{fig:conclusion}
\end{figure}

One other result presented in Chapter \ref{sec:paper1} was that nighttime occurrence of FAIs was also higher for time intervals with a negative IMF \(B_y\) component, Figure \ref{fig:conclusion}.  This could be due to the control that the \(B_y\) component exerts over ionospheric convection patterns, as explained below.  In a classical two-cell convection pattern with predominantly negative IMF \(B_z\), the plasma flows antisunward from dayside to nightside across the terminator.  In this configuration, the plasma flow, \(\vec{V}_E\), and the density gradient, \(\vec{G}\), are antiparallel, the least favorable orientation for GDI growth.  However, with a significant IMF \(B_y\) component, the orientation of the convection cells rotates such that plasma no longer convects directly antisunward, creating a situation where GDI is more favorable and plasma structures can develop more readily.  Additionally, a significant IMF \(B_y\) component can contribute to the formation of polar patches by creating convection perturbations that separate high density patches from the daytime reservoir, as described in Section \ref{sec:lit_patches}.  In this way, the IMF \(B_y\) component may be indirectly responsible for the increased observation of backscatter.  If patch occurrence increases, it can contribute to the nighttime background density, as described above, which can improve propagation conditions so that FAIs can be observed by 
HF radars.
